---
title: "Quiz1 - programming with R"
author: "Oliver Belmans"
date: "8/18/2017"
output: html_document
---

# 1
```{r}
cube <- function(x, n) {
        x^3
}

cube(3)
```

# 2
```{r}
x <- 1:10
if(x > 5) {
        x <- 0
}
```

# 3
```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
z <- 10
f(3)
```

# 4
```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}

y
```

# 5
```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```
f

# 6 
Whats an environment in R?
* a collection of symbol/value pairs

# 7 
The R language uses what type of scoping rule for resolving free variables?
* lexical scoping

# 8
How are free variables in R functions resolved?
- The values of free variables are searched for in the environment in which the function was defined

# 9
What is one of the consequences of the scoping rules used in R?
- All objects must be stored in memory

# 10
In R, what is the parent frame?
- 

